---
title: "Patent Applications in Different Countries"
author: "Ke Wang"
date: "February 17, 2015"
output: ioslides_presentation
---

## A Shiny-App to Visualize Patent Filings from Each Country

- Number of patents has always been a widely-used economic indicator that measures a country's capability to innovate.

- Both absolute number of filings and trend are important, as they tell different stories.


## Data

We gathered patent filing data that the World Bank Published for the following countries:

- United States
- United Kingdom
- Japan
- Russia
- France
- Germany
- China

The data covers patent filings from 1960 to 2012.

## Number of Patents Filed from Each Country

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
data <- read.csv("raw.csv")
  normalized <- summarise(group_by(data, country), base=min(applications, na.rm=TRUE))
  data <- merge(data, normalized, by=c('country'))
  data$normalized <- data$applications / data$base
```

```{r message=FALSE,warning=FALSE}
qplot(year, applications, data=data, color=country, geom=c('line'))
```

## Trend of Patents Filed from Each Country

```{r, message=FALSE,warning=FALSE}
qplot(year, normalized, data=data,color=country, geom=c('line'))
```

## Conclusion

From the charts, we can draw the following conclusions

- Japan and US had long been leaders in patent filings before China surpassed both around 2010.
- The rise in patent filings from China was in a fast pace that none of the other countries had seen before.

More detail is available at <https://wangcaillc.shinyapps.io/patenttrend/>.